Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-10 main.tex
Notes

@@

The {\em result} of a machine state $\mach$ with respect to a step function
$\mathord{\stepsto} \in \MACHS \rightharpoonup \MACHS$ is a state $\mach_n$
such that $\mach \manystepsto \mach_n$ and $\mach_n$ cannot step any
further.

@@

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by $\contour$.
\iftext\bcp{Spell it out formally.}\fi

Formally, a {\em policy}
$\polname \in \CONTOURS \rightarrow (\MACHS \rightarrow \MACHS)$ is a
function from contours to step functions (partial functions on $\MACHS$)
that, wherever they are defined, agree with $\stepstounderfull$.  That is,
it represents an enforcement mechanism that sometimes halts programs earlier
than the bare step relation does, but that agrees with the bare step
relation when it allows evaluation to proceed.  We write
$\mach_1 \stepstounder{\pol{\contour}} \mach_2$ for
$\pol{\contour}(\mach_1) = \mach_2$.

>>>>

\iftext
\section{Introduction}

\bcp{How about coining the term ``lockstep noninterference'' and then saying
that we study several variants...?}

\fi

@@

The {\em result} of a machine state $\mach$ with respect to a step function
$\mathord{\stepsto} \in \MACHS \rightharpoonup \MACHS$ is a state $\mach_n$
such that $\mach \manystepsto \mach_n$ and $\mach_n$ cannot step any
further.  \bcp{No halting!}

@@

\subsection{Policies}

\bcp{Try this:
  \begin{itemize}
  \item two separate axes: high/low and observable/hidden
  \item both part of contours
  \end{itemize}
}

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = \LOW$, then $\mach(\component)
= \mach'(\component)$.

Formally, a {\em policy}
$\polname \in \CONTOURS \rightarrow (\MACHS \rightarrow \MACHS)$ is a
function from contours to step functions (partial functions on $\MACHS$)
that, wherever they are defined, agree with $\stepstounderfull$.  That is,
it represents an enforcement mechanism that sometimes halts programs earlier
than the bare step relation does, but that agrees with the bare step
relation when it allows evaluation to proceed.  We write
$\mach_1 \stepstounder{\pol{\contour}} \mach_2$ for
$\pol{\contour}(\mach_1) = \mach_2$.  \bcp{It should also return a contour!}
